Appendix

### 2023-06-28 manuscript/appendix.qmd
Update PDF format

## Appendix A: model predictors {.appendix .unnumbered}

{{< include _appendix/_model-predictors.qmd >}}

## Appendix B: model details {.appendix .unnumbered}

{{< include _appendix/_model-details.qmd >}}

## Appendix C: convergence diagnostics {.appendix .unnumbered}

{{< include _appendix/_model-diagnostics.qmd >}}

## Appendix D: frequency and language exposure as separate predictors {.appendix .unnumbered}

@@

## Appendix E: frequency and language exposure as separate predictors {.appendix .unnumbered}

>>>>

## Appendix A: frequency and language exposure as separate predictors {.appendix .unnumbered}

@@

## Appendix B: frequency and language exposure as separate predictors {.appendix .unnumbered}
